\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}

\name{Zhouyang Jia}

\begin{document}
\vspace{-1em}

\begin{rSubsection}
    {Assistant Professor}
    {College of Computer Science}
    {National University of Defense Technology}
    {+86 15973156535}
    {jiazhouyang@nudt.edu.cn}
    {109 Deya Road, Changsha, China, 410072}
\end{rSubsection}

\begin{rSection}{Education}
    {Ph.D. in Software Engineering @ National University of Defense Technology} \hfill {2016.02 -- 2020.12}

    {Visiting Scholar @ University of Kentucky, USA} \hfill {2018.08 -- 2020.08}

    {M.E. in Software Engineering @ National University of Defense Technology} \hfill {2013.09 -- 2015.12}

    {B.E. in Computer Science @ National University of Defense Technology} \hfill {2009.09 -- 2013.07}
\end{rSection}

\begin{rSection}{Selected Awards}
    {ACM SIGSOFT Distinguished Paper Award @ ICSE'23} \hfill {2023}

    {IEEE TCSE Distinguished Paper Award @ SANER'23} \hfill {2023}

    {CCF Excellent Doctoral Incentive Program Nomination Award} \hfill {2022}

    {Honorable Mention Award @ ICPC'21} \hfill {2021}

    {IEEE TCSE Distinguished Paper Award @ SANER'18} \hfill {2018}

    {CCF Elite Collegiate Award} \hfill {2012}
\end{rSection}

\begin{rSection}{Selected Publications}
    \subsection*{2023}

    Teng Wang*, \textbf{Zhouyang Jia}*, Shanshan Li, Si Zheng, Yue Yu, Erci Xu, Shaoliang Peng, and Xiangke Liao. Understanding and Detecting On-the-Fly Configuration Bugs [C]. In: Proceedings of the 45th International Conference on Software Engineering. \textbf{ICSE 2023}. To appear. (\textbf{Distinguished Paper Award}, *Co-first Author).

    Haochen He, Erci Xu, Shanshan Li, \textbf{Zhouyang Jia}, Si Zheng, Yue Yu, Jun Ma, and Xiangke Liao. When Database Meets New Storage Devices: Understanding and Exposing Performance Mismatches via Configurations [C]. In: Proceedings of the 49th International Conference on Very Large Data Bases. \textbf{VLDB 2023}. To appear.

    Yingwei Ma, Yue Yu, Shanshan Li, \textbf{Zhouyang Jia}, Jun Ma, Rulin Xu, Wei Dong, and Xiangke Liao. MulCS: Towards a Unified Deep Representation for Multilingual Code Search [C]. In: Proceedings of the 30th International Conference on Software Analysis, Evolution and Reengineering. \textbf{SANER 2023}. To appear. (\textbf{Distinguished Paper Award}).

    \subsection*{2022}

    Haochen He*, \textbf{Zhouyang Jia}*, Shanshan Li, Yue Yu, Chenglong Zhou, Qing Liao, Ji Wang, and Xiangke Liao. Multi-Intention-Aware Configuration Selection for Performance Tuning [C]. In: Proceedings of the 44th International Conference on Software Engineering. \textbf{ICSE 2022}. 1431-1442. (*Co-first Author).

    Deze Wang, \textbf{Zhouyang Jia}, Shanshan Li, Yue Yu, Yun Xiong, Wei Dong, and Xiangke Liao. Bridging Pre-trained Models and Downstream Tasks for Source Code Understanding [C]. In: Proceedings of the 44th International Conference on Software Engineering. \textbf{ICSE 2022}. 287-298.

    \subsection*{2021}

    \textbf{Zhouyang Jia}, Shanshan Li, Tingting Yu, Chen Zeng, Erci Xu, Xiaodong Liu, Ji Wang, and Xiangke Liao. DepOwl: Detecting Dependency Bugs to Prevent Compatibility Failures [C]. In: Proceedings of the 43rd International Conference on Software Engineering. \textbf{ICSE 2021}. 86-98.

    Wang Li*, \textbf{Zhouyang Jia}*, Shanshan Li, Yuanliang Zhang, Teng Wang, Erci Xu, Ji Wang, and Xiangke Liao. Challenges and opportunities: an in-depth empirical study on configuration error injection testing [C]. In: Proceedings of the 30th ACM SIGSOFT International Symposium on Software Testing and Analysis. \textbf{ISSTA 2021}. 478-490. (*Co-first author).

    Shulin Zhou, Xiaodong Liu, Shanshan Li, \textbf{Zhouyang Jia}, Yuanliang Zhang, Teng Wang, Wang Li, and Xiangke Liao. ConfInLog: Leveraging Software Logs to Infer Configuration Constraints [C]. In: Proceedings of the 29th IEEE/ACM International Conference on Program Comprehension. \textbf{ICPC 2021}. 94-105. (\textbf{Honorable Mention Award})

    \subsection*{2020}

    Haochen He*, \textbf{Zhouyang Jia}*, Shanshan Li, Erci Xu, Tingting Yu, Yue Yu, Ji Wang, and Xiangke Liao. CP-Detector: Using Configuration-related Performance Properties to Expose Performance Bugs [C]. In: Proceedings of the 35th IEEE/ACM International Conference on Automated Software Engineering. \textbf{ASE 2020}. 623-634. (*Co-first Author).

    Shanshan Li, Xu Niu, \textbf{Zhouyang Jia}, Xiangke Liao, Ji Wang, and Tao Li. Guiding log revisions by learning from software evolution history [J]. Empirical Software Engineering. \textbf{EMSE 2020}. 25: 2302–2340.

    \subsection*{2019}

    \textbf{Zhouyang Jia}, Shanshan Li, Tingting Yu, Xiangke Liao, Ji Wang, Xiaodong Liu, and Yunhuai Liu. Detecting Error-Handling Bugs without Error Specification Input [C]. In: Proceedings of the 34th IEEE/ACM International Conference on Automated Software Engineering. \textbf{ASE 2019}. 213-225.

    \textbf{Zhouyang Jia}, Shanshan Li, Tingting Yu, Xiangke Liao, and Ji Wang. Automatically detecting missing cleanup for ungraceful exits [C]. In: Proceedings of the 27th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering. \textbf{ESEC/FSE 2019}. 751–762.

    \subsection*{2018}

    \textbf{Zhouyang Jia}, Shanshan Li, Xiaodong Liu, Xiangke Liao, and Yunhuai Liu. SMARTLOG: Place error log statement by deep understanding of log intention [C]. In: Proceedings of the 25th International Conference on Software Analysis, Evolution and Reengineering. \textbf{SANER 2018}. 61-71. (\textbf{Distinguished Paper Award}).

    Shanshan Li, Xu Niu, \textbf{Zhouyang Jia}, Ji Wang, Haochen He, and Teng Wang. Logtracker: learning log revision behaviors proactively from software evolution history [C]. In: Proceedings of the 26th Conference on Program Comprehension. \textbf{ICPC 2018}. 178–188.
\end{rSection}

\end{document}
